Pareto-Optimal Multistate Protein Design using Tree Graphical Models

### 2013-01-04 docs/tex/experiments.tex
Replaced with verbatim outputs

\subsubsection{Simulation Experiment 5 : Random feature space tied}
Like~\ref{sim:randprobstied} but the feature space is random
\label{sim:randfeatstied}

\subsubsection{Simulation Experiment 6 :  Random feature space untied}
Like~\ref{sim:randprobsuntied} but the feature space is random
\label{sim:randfeatsuntied}

\subsubsection{Simulation Experiment 7: Vary Seq space }
\label{sim:seqspace}
Increase the sequence space using random untied feature space as in ~\ref{sim:randfeatsuntied}. Will supply different seq space values. 2,4,16,20 are the values that are goint to be used.

\subsubsection{Simulation Experiment 8: Seq space 20, Vary seq length}
\label{sim:seqlen}
Set the sequence space to be 20 and vary the sequence length from 2^2,2^16

\subsubsection{Simulation Experiment 9 : Jointly vary seq space and length}
\label{sim:seqspacelen}
Jointly vary the sequence space and sequence length,

\subsubsection{Simulation Experiment 10: Vary Feat space }
\label{sim:featspace}
Keeping the seq space at 20, vary feat space from 5-10-25-50

\subsubsection{Simulation Experiment 11: Vary Feat space and sequence length}
\label{sim:featspacelen}
Keeping the seq space at 20, vary feat space from 5-10-25-50, sequence length from 2^2,2^16

\subsubsection{Simulation Experiment : K-way multistate design}

>>>>

\subsubsection{Simulation Experiment 5 : Random feature space tied}
Like~\ref{sim:randprobstied} but the feature space is randomized while the parameters between differnent amino acids are tied together. 
\label{sim:randfeatstied}

\subsubsection{Simulation Experiment 6 :  Random feature space untied}
Like~\ref{sim:randprobsuntied} but the feature space is randomized while the different amino acids are untied. This is the most general of the previous settings. 
\label{sim:randfeatsuntied}

\begin{center}
    \begin{tabular}{| c | c | c | c |}
    \hline
    Experiment & Brute & Pareto \\ \hline
    Sim~\ref{sim:toy} & 0.907 & 0.003 \\ \hline
    Sim~\ref{sim:randprobs} & 0.986 & 0.006 \\ \hline
    Sim~\ref{sim:randprobstied} & 0.912 & 0.004 \\ \hline
    Sim~\ref{sim:randprobsuntied} & 0.903 & 0.0034\\ \hline
    Sim~\ref{sim:randfeatstied} & 0.921 & 0.011 \\ \hline
    Sim~\ref{sim:randfeatsuntied} & 0.910 & 0.006 \\ \hline
    \hline
    \end{tabular}
\end{center}

\subsubsection{Simulation Experiment 7: Vary Seq space }
\label{sim:seqspace}
Increase the sequence space using random untied feature space as in ~\ref{sim:randfeatsuntied}. Will supply different seq space values. 2,4,16,20 are the values that are goint to be used.
\begin{verbatim}
sim3_seqspace_2_0pareto : 0.017 seconds
sim3_seqspace_2_1pareto : 0.005 seconds
sim3_seqspace_2_2pareto : 0.007 seconds
sim3_seqspace_4_0pareto : 0.022 seconds
sim3_seqspace_4_1pareto : 0.021 seconds
sim3_seqspace_4_2pareto : 0.015 seconds
sim3_seqspace_8_0pareto : 0.040 seconds
sim3_seqspace_8_1pareto : 0.069 seconds
sim3_seqspace_8_2pareto : 0.061 seconds
sim3_seqspace_16_0pareto : 0.338 seconds
sim3_seqspace_16_1pareto : 0.213 seconds
sim3_seqspace_16_2pareto : 0.214 seconds
sim3_seqspace_20_0pareto : 0.370 seconds
sim3_seqspace_20_1pareto : 0.463 seconds
sim3_seqspace_20_2pareto : 0.284 seconds
\end{verbatim}

\subsubsection{Simulation Experiment 8: Seq space 20, Vary seq length}
\label{sim:seqlen}
Set the sequence space to be 20 and vary the sequence length from $2^2$  to $2^7$
\begin{verbatim}
sim3_seqlen_4_0pareto : 0.047 seconds
sim3_seqlen_4_1pareto : 0.011 seconds
sim3_seqlen_4_2pareto : 0.029 seconds
sim3_seqlen_16_0pareto : 0.621 seconds
sim3_seqlen_16_1pareto : 0.857 seconds
sim3_seqlen_16_2pareto : 0.499 seconds
sim3_seqlen_32_0pareto : 2.343 seconds
sim3_seqlen_32_1pareto : 2.344 seconds
sim3_seqlen_32_2pareto : 2.409 seconds
sim3_seqlen_64_0pareto : 8.683 seconds
sim3_seqlen_64_1pareto : 10.716 seconds
sim3_seqlen_64_2pareto : 11.068 seconds
sim3_seqlen_128_0pareto : 39.451 seconds
sim3_seqlen_128_1pareto : 40.050 seconds
sim3_seqlen_128_2pareto : 33.411 seconds
\end{verbatim}
%

\subsubsection{Simulation Experiment 9 : Jointly vary seq space and length}
\label{sim:seqspacelen}
Jointly vary the sequence space and sequence length, 
\begin{verbatim}
sim3_seqspacelen_4_2_0pareto : 0.001 seconds
sim3_seqspacelen_4_2_1pareto : 0.001 seconds
sim3_seqspacelen_4_4_0pareto : 0.000 seconds
sim3_seqspacelen_4_4_1pareto : 0.004 seconds
sim3_seqspacelen_4_8_0pareto : 0.010 seconds
sim3_seqspacelen_4_8_1pareto : 0.003 seconds
sim3_seqspacelen_4_16_0pareto : 0.032 seconds
sim3_seqspacelen_4_16_1pareto : 0.014 seconds
sim3_seqspacelen_16_2_0pareto : 0.019 seconds
sim3_seqspacelen_16_2_1pareto : 0.017 seconds
sim3_seqspacelen_16_4_0pareto : 0.040 seconds
sim3_seqspacelen_16_4_1pareto : 0.039 seconds
sim3_seqspacelen_16_8_0pareto : 0.144 seconds
sim3_seqspacelen_16_8_1pareto : 0.102 seconds
sim3_seqspacelen_16_16_0pareto : 0.375 seconds
sim3_seqspacelen_16_16_1pareto : 0.398 seconds
sim3_seqspacelen_32_2_0pareto : 0.012 seconds
sim3_seqspacelen_32_2_1pareto : 0.044 seconds
sim3_seqspacelen_32_4_0pareto : 0.109 seconds
sim3_seqspacelen_32_4_1pareto : 0.156 seconds
sim3_seqspacelen_32_8_0pareto : 0.290 seconds
sim3_seqspacelen_32_8_1pareto : 0.389 seconds
sim3_seqspacelen_32_16_0pareto : 1.166 seconds
sim3_seqspacelen_32_16_1pareto : 1.821 seconds
sim3_seqspacelen_64_2_0pareto : 0.195 seconds
sim3_seqspacelen_64_2_1pareto : 0.191 seconds
sim3_seqspacelen_64_4_0pareto : 0.567 seconds
sim3_seqspacelen_64_4_1pareto : 0.458 seconds
sim3_seqspacelen_64_8_0pareto : 1.594 seconds
sim3_seqspacelen_64_8_1pareto : 1.679 seconds
sim3_seqspacelen_64_16_0pareto : 7.087 seconds
sim3_seqspacelen_64_16_1pareto : 5.645 seconds
sim3_seqspacelen_128_2_0pareto : 0.713 seconds
sim3_seqspacelen_128_2_1pareto : 0.670 seconds
sim3_seqspacelen_128_4_0pareto : 2.135 seconds
sim3_seqspacelen_128_4_1pareto : 2.418 seconds
sim3_seqspacelen_128_8_0pareto : 6.247 seconds
sim3_seqspacelen_128_8_1pareto : 6.642 seconds
sim3_seqspacelen_128_16_0pareto : 23.922 seconds
sim3_seqspacelen_128_16_1pareto : 24.432 seconds
\end{verbatim}

\subsubsection{Simulation Experiment 10: Vary Feat space }
\label{sim:featspace}
Keeping the seq space at 20 and seq len at 16. vary feat space from 5-10-25-50

\begin{verbatim}
sim3_featspace_5_0pareto : 0.344 seconds
sim3_featspace_5_1pareto : 0.426 seconds
sim3_featspace_5_2pareto : 0.499 seconds
sim3_featspace_10_0pareto : 0.543 seconds
sim3_featspace_10_1pareto : 0.706 seconds
sim3_featspace_10_2pareto : 0.657 seconds
sim3_featspace_25_0pareto : 0.632 seconds
sim3_featspace_25_1pareto : 0.493 seconds
sim3_featspace_25_2pareto : 0.536 seconds
sim3_featspace_50_0pareto : 0.543 seconds
sim3_featspace_50_1pareto : 0.676 seconds
sim3_featspace_50_2pareto : 0.586 seconds
\end{verbatim}

\subsubsection{Simulation Experiment 11: Vary Feat space and sequence length}
\label{sim:featspacelen}
Keeping the seq space at 20, vary feat space from 5-10-25-50, sequence length from seqlen to 64.

\begin{verbatim}
sim3_featspacelen_4_5_0pareto : 0.030 seconds
sim3_featspacelen_4_5_1pareto : 0.037 seconds
sim3_featspacelen_4_10_0pareto : 0.046 seconds
sim3_featspacelen_4_10_1pareto : 0.045 seconds
sim3_featspacelen_4_25_0pareto : 0.056 seconds
sim3_featspacelen_4_25_1pareto : 0.037 seconds
sim3_featspacelen_4_50_0pareto : 0.028 seconds
sim3_featspacelen_4_50_1pareto : 0.071 seconds
sim3_featspacelen_16_5_0pareto : 0.338 seconds
sim3_featspacelen_16_5_1pareto : 0.419 seconds
sim3_featspacelen_16_10_0pareto : 0.536 seconds
sim3_featspacelen_16_10_1pareto : 0.699 seconds
sim3_featspacelen_16_25_0pareto : 0.621 seconds
sim3_featspacelen_16_25_1pareto : 0.515 seconds
sim3_featspacelen_16_50_0pareto : 0.584 seconds
sim3_featspacelen_16_50_1pareto : 0.752 seconds
sim3_featspacelen_32_5_0pareto : 2.014 seconds
sim3_featspacelen_32_5_1pareto : 2.501 seconds
sim3_featspacelen_32_10_0pareto : 2.142 seconds
sim3_featspacelen_32_10_1pareto : 2.176 seconds
sim3_featspacelen_32_25_0pareto : 2.277 seconds
sim3_featspacelen_32_25_1pareto : 2.080 seconds
sim3_featspacelen_32_50_0pareto : 2.555 seconds
sim3_featspacelen_32_50_1pareto : 1.944 seconds
sim3_featspacelen_64_5_0pareto : 8.940 seconds
sim3_featspacelen_64_5_1pareto : 10.489 seconds
sim3_featspacelen_64_10_0pareto : 9.777 seconds
sim3_featspacelen_64_10_1pareto : 8.458 seconds
sim3_featspacelen_64_25_0pareto : 10.321 seconds
sim3_featspacelen_64_25_1pareto : 9.168 seconds
sim3_featspacelen_64_50_0pareto : 9.095 seconds
sim3_featspacelen_64_50_1pareto : 8.893 seconds
\end{verbatim}
%
\subsubsection{Simulation Experiment : K-way multistate design}
